\documentclass[a4paper,10pt]{article}

% --- Packages ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=0.9cm]{geometry}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{tcolorbox}
\usepackage{anyfontsize} % Support custom font sizes

% --- Colors (Slate & Blue theme) ---
\definecolor{primary-color}{HTML}{0f172a}
\definecolor{accent-color}{HTML}{2563eb}
\definecolor{text-color}{HTML}{1e293b}
\definecolor{text-light}{HTML}{64748b}
\definecolor{sidebar-bg}{HTML}{f8fafc}

% --- Settings ---
\pagestyle{empty}
\setlist[itemize]{leftmargin=*, nosep, label=\color{accent-color}\textbullet, itemsep=1.5pt}
\hypersetup{colorlinks=true, urlcolor=text-color, hidelinks}

% --- Section Styling ---
\titleformat{\section}{\color{primary-color}\normalsize\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}

\newcommand{\sidebarsection}[1]{
    \vspace{6pt}
    {\color{accent-color}\scriptsize\bfseries\uppercase{#1}}
    \vspace{2pt}
    \hrule height 0.5pt
    \vspace{3pt}
}

% --- Document Start ---
\begin{document}

% --- Header ---
\noindent
\begin{minipage}[t]{0.48\textwidth}
    {\fontsize{26pt}{26pt}\selectfont \bfseries \color{primary-color} SHARAN} \\
    \vspace{1pt}
    {\color{accent-color}\bfseries \normalsize Cloud / DevOps Engineer}
\end{minipage}%
\begin{minipage}[t]{0.52\textwidth}
    \raggedleft
    \fontsize{7.5pt}{8.5pt}\selectfont \color{text-color}
    \faEnvelope \ \href{mailto:sharanboominathan@gmail.com}{sharanboominathan@gmail.com} \quad \faPhone \ 73058 85870 \\
    \faMapMarker \ Chennai, India \\
    \faGlobe \ \href{https://sharanboominathan.github.io/Sharan_Portfolio/}{\fontsize{7pt}{8pt}\selectfont Portfolio Profile: sharanboominathan.github.io/Sharan\_Portfolio/} \\
    \faLinkedin \ \href{https://www.linkedin.com/in/sharan-b-956422281}{\fontsize{7pt}{8pt}\selectfont LinkedIn Profile: linkedin.com/in/sharan-b-956422281} \\
    \faGithub \ \href{https://github.com/sharanboominathan}{\fontsize{7pt}{8pt}\selectfont GitHub Profile: github.com/sharanboominathan}
\end{minipage}

\vspace{2pt}
{\color{primary-color}\hrule height 1.2pt}
\vspace{6pt}

% --- Main Layout ---
\noindent
\begin{minipage}[t]{0.28\textwidth}
    \begin{tcolorbox}[colback=sidebar-bg, colframe=sidebar-bg, arc=4pt, boxrule=0pt, left=4pt, right=4pt, top=4pt, bottom=4pt]
        \sidebarsection{Professional Summary}
        \fontsize{7.5pt}{8.8pt}\selectfont \color{text-color}
        Highly skilled Cloud \& DevOps Engineer with 3+ years of experience in architecting and managing production-scale cloud infrastructure on Azure and AWS. Expert in Kubernetes (AKS/EKS), Terraform, and CI/CD.

        \sidebarsection{Key Metrics}
        \begin{itemize}[itemsep=1pt]
            \item \fontsize{7.2pt}{8pt}\selectfont 25+ Cloud-native apps
            \item \fontsize{7.2pt}{8pt}\selectfont 20+ Production domains
            \item \fontsize{7.2pt}{8pt}\selectfont 30+ Production deployments
            \item \fontsize{7.2pt}{8pt}\selectfont 40\% Faster CI/CD ops
            \item \fontsize{7.2pt}{8pt}\selectfont 30\% Lower downtime
        \end{itemize}

        \sidebarsection{Technical Skills}
        \fontsize{7.2pt}{8pt}\selectfont \color{text-color}
        \textbf{Cloud \& DevOps:} \\
        Azure (AKS, ACR, DNS, Front Door, WAF), AWS, Docker, Kubernetes, CI/CD, Nginx, cert-manager. \\
        \vspace{2pt}
        \textbf{Development:} \\
        Python, Django, REST APIs, Microservices, HTML/CSS, JS. \\
        \vspace{2pt}
        \textbf{AI \& ML:} \\
        Azure ML, RAG-based chatbots, NLP. \\
        \vspace{2pt}
        \textbf{Databases:} \\
        MySQL, Oracle.

        \sidebarsection{Education}
        \fontsize{7.2pt}{8pt}\selectfont \color{text-color}
        \textbf{B.E. Computer Science} \\
        Pondicherry University, Chennai \\
        2018 - 2022

        \sidebarsection{Key Achievements}
        \begin{itemize}[itemsep=1pt]
            \item \fontsize{7pt}{7.5pt}\selectfont Shared AKS for 25+ apps.
            \item \fontsize{7pt}{7.5pt}\selectfont SSL automation (20+ domains).
            \item \fontsize{7pt}{7.5pt}\selectfont AI chatbot \& RAG rollout.
            \item \fontsize{7pt}{7.5pt}\selectfont Azure Front Door Routing.
        \end{itemize}
    \end{tcolorbox}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.69\textwidth}
    \section{Professional Experience}
    \textbf{Cloud / DevOps Engineer} \hfill {\color{accent-color} BigFix} \\
    \fontsize{8.5pt}{9.5pt}\selectfont May 2025 -- Present \hfill Chennai, India \\
    \vspace{2pt}
    \begin{itemize}[itemsep=1.5pt]
        \item \fontsize{8.5pt}{9.5pt}\selectfont Designed and deployed 25+ production Django and SaaS platforms using Azure, Docker and Kubernetes (AKS).
        \item \fontsize{8.5pt}{9.5pt}\selectfont Architected a multi-tenant Kubernetes platform hosting multiple business applications from a shared AKS + ACR infrastructure.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Implemented Azure Front Door with WAF for global routing, SSL termination and perimeter security.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Built and operated centralized SSL automation using Nginx Ingress and cert-manager across all production domains.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Delivered multiple public production platforms with full DevOps lifecycle ownership.
    \end{itemize}

    \section{Projects \& Deployments}
    
    \textbf{BigFix Multi-Domain Platform} \\
    \fontsize{8.2pt}{9pt}\selectfont AKS platform hosting 20+ subdomains with automated DNS, SSL, and monitoring. \\
    {\color{text-light}\textit{\fontsize{7.2pt}{8pt}\selectfont Azure AKS, Nginx, cert-manager, GitHub Actions}} \\
    
    \vspace{3pt}
    \textbf{RepairWorks \& WarrantyWorks} \\
    \fontsize{8.2pt}{9pt}\selectfont Enterprise SaaS for repair management. Full-stack Django on Kubernetes with microservices. \\
    {\color{text-light}\textit{\fontsize{7.2pt}{8pt}\selectfont Django, MySQL, Docker, Azure AKS, CI/CD}} \\

    \vspace{3pt}
    \textbf{Warrantify \& Assurify} \\
    \fontsize{8.2pt}{9pt}\selectfont AI-enabled warranty platforms with chatbot integration and claim workflows. \\
    {\color{text-light}\textit{\fontsize{7.2pt}{8pt}\selectfont Python, Django, Azure, AI integration}} \\

    \vspace{3pt}
    \textbf{BIGFIX AI Platform} \\
    \fontsize{8.2pt}{9pt}\selectfont Enterprise AI with Azure ML integration and local RAG-based support chatbot. \\
    {\color{text-light}\textit{\fontsize{7.2pt}{8pt}\selectfont Azure ML, Python, RAG, AI/ML pipelines}} \\

    \section{Roles \& Responsibilities}
    \begin{itemize}[itemsep=1pt]
        \item \fontsize{8.5pt}{9.5pt}\selectfont Deploying and managing AWS and Azure (AKS, ACR, DNS, Bastion, Monitor) resources.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Containerizing apps with Docker \& Kubernetes, configuring Nginx Ingress for routing.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Managing SSL with cert-manager + Let’s Encrypt for secure multi-domain deployments.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Ensuring scalability, cost efficiency, and high availability in cloud solutions.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Architecting and deploying multi-tenant Kubernetes platforms for SaaS applications.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Implementing Azure Front Door with WAF for global routing and security.
        \item \fontsize{8.5pt}{9.5pt}\selectfont Building and operating centralized SSL automation for multiple production domains.
    \end{itemize}

\end{minipage}

\end{document}
